---
title: "Test Design report"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: 
      version: 5
      bg: "#F9F9F9"
      fg: "#5e5ea3"
      primary: "#5e5ea3"
      base_font: !expr bslib::font_google("Lato")
      code_font: !expr bslib::font_google("JetBrains Mono")
params:
  design_powerthreshold: NA
  design_final_sizes: NA
  design_nclusters: NA
  design_paramprev: NA
  design_paramicc: NA
  design_paramsims: NA
  design_poweroutput: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(kableExtra)

set.seed(10)
```

## *This is just a test document for now *

### Sample size tables
Maybe here would be nice to provide the sample size table for the selected power threshold?

You selected a power threshold of `r as.numeric(params$design_powerthreshold)*100`%. 
```{r}
# pow_threshold <- params$design_powerthreshold
# 
# pow_threshold
```

### Final cluster sizes
Based on the values you entered, you selected `r params$design_nclusters` clusters for the study design. The final adjusted sample sizes based on the target sample size and expected drop-out proportion in each cluster are shown below:

```{r}
# df <- as.data.frame(params$design_final_sizes)
df_final_sizes <- params$design_final_sizes

df_final_sizes %>% 
  knitr::kable("html") %>%
  kable_styling(bootstrap_options = "striped", 
                position = "left",
                full_width = F) 

# n <- params$design_nclusters
# 
# n
```

#### Estimated power 
To estimate power we used the [DRpower package](https://mrc-ide.github.io/DRpower) with the following user-selected parameters: 

- The final sample sizes for the `r params$design_nclusters` clusters (shown above)
- Prevalence of `r params$design_paramprev` 
- Intra-cluster correlation of `r params$design_paramicc` 
- `r params$design_paramsims` simulations

The estimated power is presented below:
```{r}
power_output <- params$design_poweroutput
param_prev <- params$design_paramprev
param_icc <- params$design_paramicc
param_sims <- params$design_paramsims

power_output %>% 
  ggplot() +
  geom_segment(aes(x = " ", xend = " ",y = lower, yend = upper), color = "black", linewidth = 1) +
  geom_point(aes(x = " ", y = power),
             size = 4,
             shape = 21,
             fill = "skyblue3") +
  geom_hline(yintercept = 0.8, color = "darkgrey", linetype = "dashed") +
  geom_text(aes(x= " ", y = 0.825, label = "80% threshold"), color = "darkgrey") +
  scale_y_continuous(labels = scales::percent_format(1), limits = c(0,1)) +
  labs(x = "",
       y = "Estimated power",
       caption = paste0("Parameters: prev=", param_prev, ", ICC=", param_icc, ", sims=", param_sims)) +
  theme_light() +
  theme(text = element_text(size = 16))
```
